$jk$-means tests

### 2016-09-01 Rmd/RenzeTest.Rmd
add ability to run with non-fixed w; revisted GMM vs kmeans test

```{r include=FALSE}
require('ggplot2')
require('reshape')
```

@@

```{r}
n<- 30
K<- 2
p<- 2
batchN<- 1000

@@

>>>>

```{r include=FALSE}
require('ggplot2')
require('reshape')
require('jkmeans')

@@

```{r}
n<- 30
K<- 2
p<- 2
batchN<- 10000

@@

###2. Run j-sparse-GMM with different j

Run 12-GMM, get average error

jk12 <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 1,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini,fixW = F)

Run 22-GMM, get average error

jk22 <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 2,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini,fixW = F)

#Conclusion:

The better performance of the k-means over GMM in terms of clustering, reported by Renze, is more likely due to fixing w=1/k in k-means.

On the other hand, we do see 1-sparse-GMM outperforms 2-sparse-GMM in clustering. This suggests focusing applying the sparsity idea in general mixture model would be a good direction.
